A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-05-21 sections/Discussion.tex
minor typos

In a practical point of view, programmers may not write the syntax $\Lambda a. e : A$ directly.
The ScopedTypeVariables extension of Haskell is effective only
when the type signature is explicitly universally quantified
(the compiler translates into an expression similar to $\Lambda a. e : A$);
otherwise the program means the normal syntax $e : \all A$,
and one may not later refer to the type variable $a$.

>>>>

In a practical point of view, programmers may not write the syntax $\Lambda a.~e : A$ directly.
The ScopedTypeVariables extension of Haskell is effective only
when the type signature is explicitly universally quantified
(the compiler translates into an expression similar to $\Lambda a.~e : A$);
otherwise the program means the normal syntax $e : \all A$,
and one may not later refer to the type variable $a$.
